---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ask

Another interface to chatGPT with R, but the goal ultimately here is to integrate
it in the R workflow by creating specialized wrappers.

For the speech to text feature you might need.

```
brew install portaudio
pip install SpeechRecognition
pip install pyAudio
```

The first one for MacOS only, not sure about other systems, hopefully the 
errors will guide you, use the `ask()` function!

## Installation

install with

``` r
pak::pak("moodymudskipper/ask")
```

## Example

```{r example}
library(ask)

ask("where is the Eiffel tower?")

follow_up("is it high?")

again()

ask_numeric("how many dwarves in Snow White?")

ask_boolean("Do birds sing?")

ask_boolean("Is the earth flat?")

ask_boolean("Does God exist")

ask_boolean("potatoe")
```

If no input is provided we use speech to text, say "stop listening" to interrupt the
recording, or wait until the time out threshold is reached.

Call `ask_document()` to query in context to the active script. For instance:
`ask_document("add roxygen2 doc to these functions")`, 
`ask_document("can this be simplified?")`,
`ask_document("rewrite this in data.table")`.

We plan to develop more such functions to help R development not only through
questions but also script creations or in place modifications that we can then review through git diffs.

Would be great to have for instance : 

* `ask_repo()`
* `ask_email()`
* `ask_calendar()`
* `ask_git()`

To do so we need to fetch the info, turn it into english text and use it to enrich
prompts.
